\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/background.tex
update 24 Dec 20.00
Update Dec 25 21:20

\LAMP allows \PO state trajectories up to a minimum percentage of 1/5 of non-empty states as well as \POstar state trajectories with different degrees of observability in the number of propositions in each state. It uses an error metric based on counting the differences in the number of precondition and effects between the ground-truth model and the learned model. In general, the results show that the accuracy of the learned models is fairly sensitive to the threshold chosen to learn the weights of the candidate formulas, and that domains that feature more conditional effects are harder to learn.

@@

\textcolor[rgb]{1.00,0.00,0.00}{Finally, we present the Learning Object-Centred Models (\textbf{\LOCM}), possibly the most distinctive learning system due to its ability of learning with minimal input knowledge.} \textbf{\LOCM} only requires the \FO action sequence of the plan trace, without need for providing any information about the predicates or the state trajectory, not even the initial or final state~\cite{CresswellMW09,cresswell2013acquiring}. The lack of available state information is overcome by exploiting assumptions about the structure of the actions. Particularly, \LOCM assumes that objects found in the same position in the header of actions are grouped as a collection of objects (sorts) whose defined set of states is captured by a parameterized Finite State Machine (FSM). The intuitive assumptions of \LOCM, like the continuity of object transitions or the association of parameters between consecutive actions in the training dataset, yield a learning model heavily reliant on the kind of domain structure. A later work, \textbf{\LOCMtwo}, extends the applicability of the \LOCM algorithm to a wider range of domains by introducing a richer representation that allows using multiple FSMs to represent the state of a sort~\cite{cresswell2011generalised}.

>>>>

\LAMP allows \PO state trajectories up to a minimum observability of 1/5 of non-empty states as well as \POstar state trajectories with different degrees of observability in the number of propositions in each state. It uses an error metric based on counting the differences in the number of precondition and effects between the ground-truth model and the learned model. In general, the results show that the accuracy of the learned models is fairly sensitive to the threshold chosen to learn the weights of the candidate formulas, and that domains that feature more conditional effects are harder to learn.

@@

\textcolor[rgb]{1.00,0.00,0.00}{Finally, we present the Learning Object-Centred Models (\textbf{\LOCM}), possibly the most distinctive learning system due to its ability of learning with minimal input knowledge.} \textbf{\LOCM} only requires the \FO action sequence of the plan trace, without need for providing any information about the predicates or the state trajectory, not even the initial or final state~\cite{CresswellMW09,cresswell2013acquiring}. The lack of available state information is overcome by exploiting assumptions about the structure of the actions. Particularly, \LOCM assumes that objects found in the same position in the header of actions are grouped as a collection of objects \textcolor[rgb]{1.00,0.00,0.00}{named \emph{sort}} whose defined set of states is captured by a parameterized Finite State Machine (FSM). The intuitive assumptions of \LOCM, like the continuity of object transitions or the association of parameters between consecutive actions in the training dataset, yield a learning model heavily reliant on the kind of domain structure. A later work, \textbf{\LOCMtwo}, extends the applicability of the \LOCM algorithm to a wider range of domains by introducing a richer representation that allows using multiple FSMs to represent the state of a \emph{sort}~\cite{cresswell2011generalised}.

### 2018-12-25 doc/aij18/major-revision/letter.tex
Update Dec 25 21:20

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{EVA ...}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{EVA ...}}

>>>>

\textcolor{blue}{The figures that appear in the third column of Table 3 for each learning system were taken from the respective published papers. They all refer to the specific experimental setup used in the evaluation of the approaches. In general, since there is not a common benchmark for the evaluation of learning approaches, each system selects the configuration of training data that best suits the particularities of the approach. Hence, all the figures in the 3rd column of Table 3 refer to the specific implementation used in the experiments. What we tried to do in this section is to somehow compare the approaches by establishing some common elements of evaluation, namely number of tested domains, size of the training data in terms of action and/or traces, degree of observability, etc.}

@@

\textcolor{blue}{A sort is a group of objects found in the same position in the header of an action. Although this was already defined in the text, we have changed the font of the word to italics and we explicitly say now this set is "named \emph{sort"}.}
